Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-14 chi2012.tex
Merged conflict

% blargh. this needs to be integrated above! 
In order to support our primary motivation to allow users to effectively consolidate and work with data from multiple sources, we performed an exploratory sequential mixed method study to help us design our contribution.  For our first pre-study we designed a semi-structured interview about which tasks and the processes people use to perform a tasks requiring multiple websites (see Section \ref{sec:prestudy1}).  We analysed the data collected from this study using a thematic approach.  From our first pre-study's qualitative analysis, we designed and performed our second study which analyses existing on data available from APIs and structured data feeds on the Web (see Section \ref{sec:prestudy2}).  The purpose of this study was to identify the degree of technical difficulty of integrating data from these sources.  We performed a statistical analysis of the features of the available data.  In the next two sections, we describe our two pre-studies.

The second study we performed an analysis on existing on data available from APIs and structured data feeds on the Web.  The purpose of this study was to identify the degree of technical difficulty of integrating data from these sources.   We describe our methodology below.

>>>>

We performed an exploratory sequential mixed method study to help us design our contribution. For our first pre-study we designed a semi-structured interview about which tasks and the processes people use to perform a tasks requiring multiple websites.  We analysed the data collected from this study using a thematic approach.

The second study we performed an analysis on existing on data available from APIs and structured data feeds on the Web, based from our first pre-study's qualitative analysis. The purpose of this study was to identify the degree of technical difficulty of integrating data from these sources. We performed a statistical analysis of the features of the available data.  In the next two sections, we describe our two pre-studies.
